A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-17 methodology.tex
reviewer2 - minor revision#2 - text bug
reviewer1 - revision#2 - link patch to vec

Figure~\ref{fig:extraction} illustrates path extraction on a simple change. The change replaces \verb+tail+ with \verb+&tail+ and \verb+head+ with \verb+head.clone()+. That is, after the change, the second argument passes a borrow of \verb+tail+ rather than sending the ownership of \verb+tail+ to the callee; and, the third argument sends a clone of head to the callee instead of sending head itself. A DFS on this tree yields three different paths, which we show in red, green, and purple. A path represents a sequence of involved non terminals. We found it crucial to record the order of nodes in the path, so that we could record that order in our datapoint embedding.

@@

        \node[draw, minimum height=0.5, fill=yellow!20] at (4.29,1.73) {Occurrences data};

        \matrix (table1) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone\\
        \# & 1 & 1 & 1 & 1 & 2 & 3 & 1 & 1 \\
        };

        \node[draw, minimum height=0.5, fill=yellow!20] at (4.12,-0.25) {Weighted data};

@@

        \matrix (table2) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,-1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone\\
        weight & 0.0004 & 2.21e-05 & 8.68e-05 & 1 & 2.60e-05 & 2.76e-05 & 4.75e-05 & 1 \\
        };

        \node[draw=none] (circlepack) at (10.5,-6.2)
            {\includegraphics[width=0.7\textwidth]{circlepack.png}};

        \node[draw=none] at (9,-2.3) {Visualizing Essence};
        \draw [-stealth,double,line width=1,color=blue!40](7,-1.6) -- (7.5,-3.4);

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right. Vectors show (above) the number of occurrences and (below) weighted occurrence counts.}
\end{figure}

@@

Multiplying the number of occurrences of all observed items in a change by their respective weights results in a vector of numbers. We call this vector the \emph{essence of change}. In this vector, the value for each item shows its importance in the change. Figure~\ref{fig:essence} shows the process of computing the essence of the code change that we saw in Figure~\ref{fig:extraction}. We have visualized this essence vector using a circle pack figure. The radius of each circle corresponds to the importance of the item inside it.

>>>>

Figure~\ref{fig:extraction} illustrates path extraction on a simple change. The change replaces \verb+tail+ with \verb+&tail+ and \verb+head+ with \verb+head.clone()+. That is, after the change, the second argument passes a borrow of \verb+tail+ rather than sending the ownership of \verb+tail+ to the callee; and, the third argument sends a clone of head to the callee instead of sending head itself. A DFS on this tree yields three different paths, which we show in red, green, and purple. A path represents a sequence of involved non terminals. It is crucial to record the order of nodes in the path, so that we could record that order in our datapoint embedding.

@@

        \node[draw, minimum height=0.5, fill=yellow!20] at (3.66,1.72) {Occurrences data};

        \matrix (table1) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone & other\\
        \# & 1 & 1 & 1 & 1 & 2 & 3 & 1 & 1 & 0\\
        };

        \node[draw, minimum height=0.5, fill=yellow!20] at (3.48,-0.25) {Weighted data};

@@

        \matrix (table2) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,-1)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone & other \\
        weight & 0.0004 & 2.21e-05 & 8.68e-05 & 1 & 2.60e-05 & 2.76e-05 & 4.75e-05 & 1 & ... \\
        };

        \node[draw, minimum height=0.5, fill=yellow!20] at (3.7,-2.25) {Essence of change};

        \node[draw=none] at (8.2,-1.95) {Result};
        \draw [-stealth,double,line width=1,color=blue!40](7,-1.6) -- (7,-2.4);

        \matrix (table3) [table,text width=6em,nodes={scale=0.45,transform shape}] at (8.5,-3)
        {
        Element & ItemFn  & Local & ExprCall & ExprReference & Path & Ident & ExprMethodCall & clone & other \\
        value & 0.0004 & 2.21e-05 & 8.68e-05 & 1 & 5.20e-05 & 8.28e-05 & 4.75e-05 & 1 & 0\\
        };

        \node[draw=none] (circlepack) at (10.5,-8.2)
            {\includegraphics[width=0.7\textwidth]{circlepack.png}};

        \node[draw=none] at (9,-4.3) {Visualizing Essence};
        \draw [-stealth,double,line width=1,color=blue!40](7,-3.6) -- (7.5,-5.4);

@@

    \caption{\label{fig:essence}Multiplying the number of occurrences of items observed in the tree by their respective weights results in the essence of change, visualized with a circle pack figure at bottom right.}
\end{figure}

@@

Multiplying the number of occurrences of all observed items in a change by their respective weights results in a vector of numbers. We call this vector the \emph{essence of change}. In this vector, the value for each item shows its importance in the change. Figure~\ref{fig:essence} shows the process of computing the essence of the code change that we saw in Figure~\ref{fig:extraction}. We have visualized this essence vector using a circle pack figure. The radius of each circle corresponds to the importance of the item inside it. The essence of change vector essentially serves as our embedding vector, transforming the patch illustrated in Figure~\ref{fig:extraction} into a fixed-sized vector as depicted in Figure~\ref{fig:essence}.
